Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release

### 2020-01-29 doc/Paper/main.tex
Fixed names, alphabetical order and added Fermilab pub.
Started addressing referee report. All changes in bold.

\newcommand{\as}[1]{{\textcolor{blue}{[AS: #1]}}}
\newcommand{\an}[1]{{\textcolor{magenta}{[AN: #1]}}}
\newcommand{\da}[1]{{\textcolor{red}{[DA: #1]}}}

@@

\usepackage[T1]{fontenc} % if needed
\usepackage{natbib}
\bibliographystyle{JHEP}
\title{Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release}

@@

\author[f]{Humna Awan,}
\author[f]{Adam Broussard,}
\author[a,g]{Jo Dunkley,}
\author[b]{Zahra Gomes,}
\author[f]{Eric Gawiser,}
\author[h]{Rachel Mandelbaum,}
\author[i,j,k,l]{Hironao Miyatake,}
\author[m]{Jeffrey A. Newman,}
\author[n]{Ignacio Sevilla,}
\author[e,o]{Sarah Skinner,}
\author[p]{Erica Wagoner}

@@

  \subsection{Pixels and maps}\label{ssec:methods.pix}
    Our $C_\ell$-based analysis requires us to make maps of different quantities. The HSC DR1 is distributed across the 6 small fields ($\lesssim20\,{\rm deg.}^2$) summarized in Table \ref{tab:field_summary}. In this case, storing maps covering the full sky down to arcminute resolution, and performing operations on them such as spherical harmonic transforms, would be computationally inefficient and unnecessary. Instead, we perform separate power spectrum measurements on each individual field, with maps defined on rectangular sky patches covering them. Furthermore, the small size of each field allows us to make use of the flat-sky approximation safely \citep{2014JCAP...10..007N}. This leads to additional gains in speed, since spherical harmonic transforms can be replaced by the far more efficient fast Fourier transforms (FFTs). Since we use a cilindrical projection with the equator at the center of each of our fields to define our flat-sky coordinates (rather than the more common gnomonic projection \citep{2002A&A...395.1077C}), the main source of curved-sky distortions occur at large latitudes, which are small ($\lesssim 1.5^\circ$) in all cases.

@@

    This defines our fiducial masks, which are shown in Figure \ref{fig:masks} for each field. As part of our analysis of systematic biases (see Section \ref{sssec:results.spectra.syst}), we also study the effect of masking regions with significant contamination from the different observing conditions (described in Section \ref{ssec:methods.syst}) on our measurements. In addition it has been observed that the NOMAD star catalog \cite{2004AAS...205.4815Z}, which is one of the datasets used to construct the bright-object mask described above, is contaminated by a small fraction of bright nearby galaxies ($\sim10\%$). To study the impact of this contamination on our clustering measurements, we therefore also estimate the angular power spectra using a more recent version of the star mask (the so-called ``Arcturus'' mask described in \cite{2018PASJ...70S...7C}).

@@

    In the absence of a sky mask, the flat-sky auto-power spectrum could be simply estimated by Fourier transforming a given map $a_{\bf l}={\rm FT}[a(\nv),{\bf l}]$ (where ${\rm FT}$ denotes a Fourier transform operation, and ${\bf l}$ is a 2D wavenumber), and averaging its modulus squared over bins of $\ell\equiv|{\bf l}|$. In any practical situation however, it will be desirable to apply weights on the map to e.g. downweight noisy areas or altogether remove pixels that haven't been observed. In this case the observed (``masked'') map is $\tilde{a}(\nv)=w(\nv)a(\nv)$, where $w(\nv)$ is a weight map. The Fourier coefficients of the observed map are therefore given by a convolution of the true Fourier coefficients with the Fourier transform of the mask, coupling different ${\bf l}$ modes in the original map. The result of using the na\"ive estimator of the power spectrum described above on the masked map is therefore a version of the true underlying power spectrum where different $\ell$s are coupled through the so-called {\sl mode-coupling matrix} $M_{\ell\ell'}$:
    \begin{equation}
      \left\langle \tilde{C}^{ab}_\ell \right\rangle = \sum_{\ell'} M_{\ell\ell'}(w_a,w_b)\,C^{ab}_{\ell'}.
    \end{equation}
    Here, $\tilde{C}^{ab}_\ell$ is the power spectrum of two observed fields $\tilde{a}=w_a\,a$ and $\tilde{b}=w_b\,b$, and $C^{ab}_\ell$ is the true power spectrum. As explicitly written above, the mode-coupling matrix depends exclusively on the properties of the survey masks \citep{2002ApJ...567....2H}, and not on the underlying signal maps. The PCL algorithm calculates the mode-coupling matrix analytically using the properties of the weight maps, and uses it to obtain an unbiased estimate of $C^{ab}_\ell$.

@@

    Following \cite{2011ApJ...736...59Z}, we parametrize the number of centrals and satellites as a function of mass as:
    \begin{align}
      &\bar{N}_c(M)=\frac{1}{2}\left[1+{\rm erf}\left(\frac{\log(M/M_{\rm min})}{\sigma_{\log M}}\right)\right],\\
      &\bar{N}_s(M)=\Theta(M-M_0)\left(\frac{M-M_0}{M_1'}\right)^\alpha,
    \end{align}
    where $\Theta(x)$ is the Heavyside step function. Furthermore, we assume that $N_c$ follows a Bernoulli distribution with probability $p=\bar{N}_c$, and that the number of satellites is Poisson-distributed with mean $\bar{N}_s$. Finally, we model the distribution of satellites to follow that of the dark matter, and therefore $u_s$ is a Navarro-Frenk-White profile, given by \cite{Navarro:1996}:
    \begin{equation}
      u_s(k|M)=\frac{\sin x\left[{\rm Si}\left((1+c)\,x\right)-{\rm Si}(x)\right]+\cos x\left[{\rm Ci}\left((1+c)x\right)-{\rm Ci}(x)\right]-\frac{\sin(cx)}{(1+c)x}}{{\rm ln}(1+c)-\frac{c}{1+c}},
    \end{equation}
    where $x=\sfrac{k R_\Delta}{c}$, $R_\Delta$ is the halo radius, $c=c(M)$ is the concentration parameter, and ${\rm Si}/{\rm Ci}$ are the sine and cosine integral functions. We define $R_\Delta$ as the radius that encloses $\Delta=200$ times the background matter density. In this work, we model the halo mass function $\sfrac{\mathrm{d}n}{\mathrm{d}M}$ following \cite{Tinker:2010}\footnote{More accurate estimates of the mass function can be obtained through the use of emulators \citep{2019ApJ...872...53M}. We verified that our analysis was not too sensitive to the choice of parameterization, and therefore we leave a more thorough study of these choices for future work.}. Furthermore, we employ the concentration-mass relation $c(M)$ (which depends on the choice of $\Delta$) derived by \cite{Duffy:2008}.

>>>>

\newcommand{\as}[1]{{\textcolor{blue}{[AS: #1]}}}
\newcommand{\an}[1]{{\textcolor{magenta}{[AN: #1]}}}
\newcommand{\da}[1]{{\textcolor{red}{[DA: #1]}}}
\newcommand{\rev}[1]{{\textbf{#1}}}

@@

\usepackage[T1]{fontenc} % if needed
\usepackage{natbib}
\bibliographystyle{JHEP}

\usepackage{eso-pic}% http://ctan.org/pkg/eso-pic
\AddToShipoutPictureBG*{%
  \AtPageUpperLeft{%
    \hspace{0.75\paperwidth}%
    \raisebox{-3.5\baselineskip}{%
      \makebox[0pt][l]{\textnormal{FERMILAB-PUB-19-626-AE}}
}}}%

\title{Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release}

@@

\author[f]{Humna Awan,}
\author[f]{Adam Broussard,}
\author[a,g]{Jo Dunkley,}
\author[f]{Eric Gawiser,}
\author[b]{Zahra Gomes,}
\author[h]{Rachel Mandelbaum,}
\author[i,j,k,l]{Hironao Miyatake,}
\author[m]{Jeffrey A. Newman,}
\author[n]{Ignacio Sevilla,}
\author[e,o]{Sarah Skinner,}
\author[p]{Erika L. Wagoner}

@@

  \subsection{Pixels and maps}\label{ssec:methods.pix}
    Our $C_\ell$-based analysis requires us to make maps of different quantities. The HSC DR1 is distributed across the 6 small fields ($\lesssim20\,{\rm deg.}^2$) summarized in Table \ref{tab:field_summary}. In this case, storing maps covering the full sky down to arcminute resolution, and performing operations on them such as spherical harmonic transforms, would be computationally inefficient and unnecessary. Instead, we perform separate power spectrum measurements on each individual field, with maps defined on rectangular sky patches covering them. Furthermore, the small size of each field allows us to make use of the flat-sky approximation safely \citep{2014JCAP...10..007N}. This leads to additional gains in speed, since spherical harmonic transforms can be replaced by the far more efficient fast Fourier transforms (FFTs). Since we use a \rev{cylindrical} projection with the equator at the center of each of our fields to define our flat-sky coordinates (rather than the more common gnomonic projection \citep{2002A&A...395.1077C}), the main source of curved-sky distortions occur at large latitudes. \rev{As all fields considered in this analysis span a rather narrow latitude range, the maximal latitudes probed after re-centering are small ($\lesssim 1.5^\circ$), and we can therefore neglect curved-sky effects.}

@@

    This defines our fiducial masks, which are shown in Figure \ref{fig:masks} for each field. As part of our analysis of systematic biases (see Section \ref{sssec:results.spectra.syst}), we also study the effect of masking regions with significant contamination from the different observing conditions (described in Section \ref{ssec:methods.syst}) on our measurements. In addition it has been observed that the NOMAD star catalog \cite{2004AAS...205.4815Z}, which is one of the datasets used to construct the bright-object mask described above, is contaminated by a small fraction of bright nearby galaxies (\rev{as described in Ref.~\cite{2018PASJ...70S..25M}, approximately $10\%$ of the objects in the NOMAD star catalog are galaxies}). To study the impact of this contamination on our clustering measurements, we therefore also estimate the angular power spectra using a more recent version of the star mask (the so-called ``Arcturus'' mask described in \cite{2018PASJ...70S...7C}).

@@

    In the absence of a sky mask, the flat-sky auto-power spectrum could be simply estimated by Fourier transforming a given map $a_{\bf l}={\rm FT}[a(\nv),{\bf l}]$ (where ${\rm FT}$ denotes a Fourier transform operation, and ${\bf l}$ is a 2D wavenumber), and averaging its modulus squared over bins of $\ell\equiv|{\bf l}|$. In any practical situation however, it will be desirable to apply weights on the map to e.g. downweight noisy areas or altogether remove pixels that haven't been observed. In this case the observed (``masked'') map is $\tilde{a}(\nv)=w(\nv)a(\nv)$, where $w(\nv)$ is a weight map. The Fourier coefficients of the observed map are therefore given by a convolution of the true Fourier coefficients with the Fourier transform of the mask, coupling different ${\bf l}$ modes in the original map. The result of using the na\"ive estimator of the power spectrum described above on the masked map is therefore a version of the true underlying power spectrum where different $\ell$s are coupled through the so-called {\sl mode-coupling matrix} $M_{\ell\ell'}$:
    \begin{equation}
      \left\langle \tilde{C}^{ab}_\ell \right\rangle = \sum_{\ell'} M_{\ell\ell'}(w_a,w_b)\,C^{ab}_{\ell'}.
    \end{equation}
    Here, $\tilde{C}^{ab}_\ell$ is the power spectrum of two observed (masked), \rev{physical} fields $\tilde{a}=w_a\,a$ and $\tilde{b}=w_b\,b$\footnote{\rev{Examples include the galaxy overdensity field or the CMB temperature anisotropies.}}, and $C^{ab}_\ell$ is the true power spectrum. As explicitly written above, the mode-coupling matrix depends exclusively on the properties of the survey masks \citep{2002ApJ...567....2H}, and not on the underlying signal maps. The PCL algorithm calculates the mode-coupling matrix analytically using the properties of the weight maps, and uses it to obtain an unbiased estimate of $C^{ab}_\ell$.

@@

    Following \cite{2011ApJ...736...59Z}, we parametrize the number of centrals and satellites as a function of mass as:
    \begin{align}
      &\bar{N}_c(M)=\frac{1}{2}\left[1+{\rm erf}\left(\frac{\log(M/M_{\rm min})}{\sigma_{\log M}}\right)\right],\\
      &\bar{N}_s(M)=\Theta(M-M_0)\left(\frac{M-M_0}{M_1'}\right)^\alpha,
    \end{align}
    where $\Theta(x)$ is the Heavyside step function. Furthermore, we assume that $N_c$ follows a Bernoulli distribution with probability $p=\bar{N}_c$, and that the number of satellites is Poisson-distributed with mean $\bar{N}_s$. Finally, we model the distribution of satellites to follow that of the dark matter, and therefore $u_s$ is a Navarro-Frenk-White profile, given by \cite{Navarro:1996}:
    \begin{equation}
      u_s(k|M)=\frac{\sin x\left[{\rm Si}\left((1+c)\,x\right)-{\rm Si}(x)\right]+\cos x\left[{\rm Ci}\left((1+c)x\right)-{\rm Ci}(x)\right]-\frac{\sin(cx)}{(1+c)x}}{{\rm ln}(1+c)-\frac{c}{1+c}},
    \end{equation}
    where $x=\sfrac{k R_\Delta}{c}$, $R_\Delta$ is the halo radius, $c=c(M)$ is the concentration parameter, and ${\rm Si}/{\rm Ci}$ are the sine and cosine integral functions. We define $R_\Delta$ as the radius that encloses $\Delta=200$ times the background matter density. In this work, we model the halo mass function $\sfrac{\mathrm{d}n}{\mathrm{d}M}$ following \cite{Tinker:2010}\footnote{More accurate estimates of the mass function can be obtained through the use of emulators \citep{2019ApJ...872...53M}. \rev{In order to test the sensitivity of our analysis to details of mass function parametrization, we have compared the constraints obtained using the mass functions from Refs.~\cite{Tinker:2010} and \cite{Tinker:2008}. We found our results to not change significantly and we therefore leave a more thorough study of these choices for future work.}}. Furthermore, we employ the concentration-mass relation $c(M)$ (which depends on the choice of $\Delta$) derived by \cite{Duffy:2008}.
